Who introduced this bug? \\ It may not have been caused by the previous commit!

### 2016-04-06 paperICSME.tex
Añadiendo algunos parrafos a Discussion

%\grex{rephrase RQs}
\begin{itemize}
     \item RQ1: How can we identify changes done to fix a bug?
     \item RQ2: How often is the previous commit the cause of the bug?
\end{itemize}

@@

The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community. Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 475 times as of April 
2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations. Hence, there is a myriad of articles that use SZZ on an ample number of scenarios. Without trying to be exhaustive, we offer several examples. Therefore, Yang et al. apply SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}. Zimmermann et al. use it for predicting bugs in large software systems~\cite{zimmermann2007predicting}. Kim et al. show how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}. Kamei et al. apply it to validate effort-aware bug-prediction models~\cite{kamei2010revisiting}. Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}. Izquierdo et al. use the SZZ algorithm to see if developers are fixing their own bugs~\cite{izquierdo2011developers}. Yin et al. use SZZ to find how many fixes to bugs introduce new bugs~\cite{yin2011fixes}. Tantithamthavorn et al. employ it to quickly identify the location of a bug~\cite{tantithamthavorn2013mining}. Fejzer et al. use it to support code review~\cite{fejzer2015supporting}. Altman et al. use it to predict whether a change is buggy at the time of a commit, evaluating the change classification techniques to address the incorrect evaluation presented by cross-validation ~\cite{altman1968financial}. Asaduzzaman et al. apply the SZZ algorithm on Android to study its maintainability~\cite{asaduzzaman2012bug}.

@@

%In addition some tools are based on SZZ too such as \cite{} 
%Finally our idea.

\section{Methodology}
\label{sec:methodology}
%We present our approach to identify how and where a bug was inserted into the source code, causing a later fix.

@@

    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considered as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates were required, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. \gema{Esto es lo que dijo uno de los revisores sobre este parrafo : "First, the rule is unclear for me. Do you mean an update to the ticket? The code? The review? Second, the rationale is unclear and unsupported. Why would such an update indicate that a bug was present?" Deberíamos modificarlo}
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected.

%    Test files in a ticket were not be analyzed, as we consider they are not a core part of the software and are used as a testing method to determine whether the code is fit for use. When the bug exclusively lies in a test file, the ticket was not considered as bug report because the software still works as expected, only test fails. \grex{no se repiten las frases?}\gema{Te refieres al inicio de cada frase o a lo que se describo en cada frase?}

@@

\begin{itemize}
    \item Exclusively blank lines
    \item Changes in the format
    \item Copied lines
    \item Changes in source code comments
    \item Updates in the version number of a file/software 
    \item These commits that were committed after the bug report was opened in Launchpad, according to to \'Sliwerski et al. ~\cite{sliwerski2005changes}.
\end{itemize}

@@

For these four projects we analyzed if bug fixes where introduce in their previous commits. For the first stage, we used the tool described in~\ref{sec:firstStage}. Each ticket was analyzed by two researchers independently. The second stage was done manually by the first author. %that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.
\gema{He calculado el tiempo medio que cada investigador (Nelson, Dorealda y Yo) ha invertido en el análisis de los tickets en
 la primera fase, usando la herrramienta. Siguiendo el orden: (4.09, 3.35, 4.12)}

\gema{He calculado la media, en minutos, del tiempo empleado en encontrar la causa del bug en cada ticket. La media a sido alrededor de 16 minutos.}
\gema{En el primer estudio realizado por Andrea y por mi con en análisis de 100 tickets; en la primera fase obtuvimos un porcentaje de acuerdo del 83\% incrementándolo hasta un 94\% tras una discusión entre ambas. En cuanto a la segunda fase, obtuvimos un 74\% de similitud entre su análisis y el mio. Después de una revisión conjunta, incrementamos ese porcentaje hasta el 90\%. En este estudio la clasificaión de la segunda fase salió (53\% ,35\% y 11\%) pero no habíamos quitado los falsos positivos.}

@@

We classify a total of 459 tickets using the tool, resulting in 917 reviews\footnote{One review was discarded as it was left empty.}. Only those tickets classified as bug reports by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits. This process requires manual inspection by researchers. In the mean, classifying a ticket takes between 5 and 10 minutes, although the amount of time decreases with experience as could be expected.

\gema{[...] se podria medir en github en tiempo que les ha llevado a cada uno entre ticket y ticket, en aquellos casos que se puedan medir y hacer una media, Que te parece?} \grex{No es muy importante, pero quedaria bien}

@@

%\grex{Tiene sentido añadir porcentajes, como he hecho a la columna de Total?}
%26-56 hours

@@

\gema{Esto es otra de las cosas que los revisores comentaron y debemos discutir: "Kim et al. [14] and Williams et al. [20] also manually analyze samples of SZZ data. However, they report much higher percentages of correct SZZ results. Potential reasons for the discrepancies should be discussed."}

@@

%\gema{Algunos de los problemas que nos hemos encontrado durante el analisis y que podrian ser resueltos de otra forma diferente a la nuestra y quizas puede que varie algo los resultados no lo se}

In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs.

@@

\gema{Defect models which identify defect-prone software models  could improve their recall and precision predicting defect-prones modules whereas they have into account our study[1, "An Extensive Comparison of Bug Prediction Approaches", 17, 27, 33, 34, 36, "BugCache for Inspections: Hit or Miss?", “Predicting Defects for Eclipse,”]}
\section{Threats to validity}
\label{sec:threats}

@@

\begin{itemize}
  \item We have not considered those tickets where the two researchers showed discordance. 
%  \begin{enumerate}
%    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
%    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
%  \end{enumerate}
    \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we have lost some \emph{actual} bug reports.
    \item There could be some lax criteria involving the subjective opinion of the researchers.
    \item Although the researchers are experienced programmers, they are not experts in the  OpenStack project, and their inexperience may have influenced the results of the analysis.
    \item We are only using part of the information that the tickets provide, like comments and text. There could be a recognized pattern in the data, unknown at first sight, that involves other parts of the information.
    \item We have used a random script to extract the tickets from Launchpad that have been reported during 2015. There could be unintended bias of the data, because many reasons, as for instance the phase of the project.
    \item In some cases, researchers may have classified the previous commit as the cause of the bug, even if this may not be the case (see discussion on additional conditions in if statements).
\end{itemize}

@@

\gema{Debemos poner en los threats to validity la subjetividad del estudio}
\section{Conclusions and Future Work}
\label{sec:conclusions}

@@

With our methodology we have identified which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools developed to prevent bugs. Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
%How to plan to apply the knowledge in a way that can benefit software engineers.
%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?

>>>>

\begin{itemize}
     \item RQ1: How can we identify changes done to fix a bug?
     \item RQ2: How often is the previous commit the cause of the bug?
\end{itemize}

@@

The SZZ algorithm (and its \emph{successors}) have had a considerable impact in the research community. Noteworthy is the fact that the paper with original the SZZ algorithm~\cite{sliwerski2005changes} has been cited, according to Google Scholar, 475 times as of April 
2016. An enhanced version of the SZZ algorithm~\cite{kim2006automatic} counts with 123 citations. Hence, there is a myriad of articles that use SZZ on an ample number of scenarios. Without trying to be exhaustive, we offer several examples. Therefore, Yang et al. apply SZZ to find what kind of bug-inducing changes are likely to become a great threat after being marked as bug-fix changes~\cite{yangbug}. Zimmermann et al. use it for predicting bugs in large software systems~\cite{zimmermann2007predicting}. Kim et al. show how to classify file changes as buggy or clean using change information features and source code terms~\cite{kim2008classifying}. Kamei et al. apply it to validate effort-aware bug-prediction models~\cite{kamei2010revisiting}. Eyolfson use it to study if time of the day and developer experience affect the probability of a commit to introduce a bug~\cite{eyolfson2011time}. Izquierdo et al. use the SZZ algorithm to see if developers are fixing their own bugs~\cite{izquierdo2011developers}. Yin et al. use SZZ to find how many fixes to bugs introduce new bugs~\cite{yin2011fixes}. Tantithamthavorn et al. employ it to quickly identify the location of a bug~\cite{tantithamthavorn2013mining}. Fejzer et al. use it to support code review~\cite{fejzer2015supporting}. Altman et al. use it to predict whether a change is buggy at the time of a commit, evaluating the change classification techniques to address the incorrect evaluation presented by cross-validation~\cite{altman1968financial}. Asaduzzaman et al. apply the SZZ algorithm on Android to study its maintainability~\cite{asaduzzaman2012bug}.

@@

\section{Methodology}
\label{sec:methodology}

@@

    \item Each time that the title or the description of a ticket describes an unexpected behaviour in the program, our criteria indicated that it was considered as a bug report. 
    \item The description of the ticket presents an optimization, deletion of a dead code or the implementation of new characteristics, we agreed not to classify it as a bug report because there is no failure. 
    \item When the ticket described that some updates in the code were required such as updates in the SO or in a version of a package/module which is being used in the code, the ticket is a bug report. We consider all tickets that require updating as bug reports, because updating a software hints to the software not operating as expected. \gema{Esto es lo que dijo uno de los revisores sobre este parrafo : "First, the rule is unclear for me. Do you mean an update to the ticket? The code? The review? Second, the rationale is unclear and unsupported. Why would such an update indicate that a bug was present?" Deberíamos modificarlo}
    \item When only test files are affected in a ticket, we classified it as not being a bug report. We consider bug errors in test files are a different type of bugs, as the software may still work as expected.

@@

\begin{itemize}
    \item Exclusively blank lines
    \item Changes in the format
    \item Copied lines
    \item Changes in source code comments
    \item Updates in the version number of a file/software 
    \item These commits that were committed after the bug report was opened in Launchpad, according to \'Sliwerski et al.~\cite{sliwerski2005changes}.
\end{itemize}

@@

For these four projects we analyzed if bug fixes where introduce in their previous commits. For the first stage, we used the tool described in~\ref{sec:firstStage}. Three different researchers, were involved in this stage, resulting that each ticket was analyzed by two of the researchers independently. The second stage was done manually by the first author. %that, we extract a total of 459 tickets from this projects, in which we should be sure that the bug fixes come from a bug report, because two of five issues are misclassified \cite{herzig2013s} and this should cause bias in our final results.

\gema{En el primer estudio realizado por Andrea y por mi con en análisis de 100 tickets; en la primera fase obtuvimos un porcentaje de acuerdo del 83\% incrementándolo hasta un 94\% tras una discusión entre ambas. En cuanto a la segunda fase, obtuvimos un 74\% de similitud entre su análisis y el mio. Después de una revisión conjunta, incrementamos ese porcentaje hasta el 90\%. En este estudio la clasificaión de la segunda fase salió (53\% ,35\% y 11\%) pero no habíamos quitado los falsos positivos.}

@@

We classify a total of 459 tickets using the tool, resulting in 917 reviews\footnote{One review was discarded as it was left empty.}. Only those tickets classified as bug reports  with a percentage of agreement of 100\% by both researchers were considered in the next stage, which analyzes if the cause of the bug was introduced in their previous commits. Thus, to measure agreement among researchers in the context of a content analysis, we have used the percent agreement variable~\cite{neuendorf2002content}. This process requires manual inspection by researchers. In the mean, classifying a ticket takes around 5 minutes, although the amount of time decreases with experience as could be expected. We have measured in Github the mean spends analyzing a ticket per each researcher, obtaining in the best case 3.35 minutes while 4.09 and 4.12 for the other two. Whereas analyzing who caused the bug, in mean, takes around 16 minutes per bug report.

\gema{He calculado el tiempo medio que cada investigador (Nelson, Dorealda y Yo) ha invertido en el análisis de los tickets en
 la primera fase, usando la herrramienta. Siguiendo el orden: (4.09, 3.35, 4.12)}
\gema{He calculado la media, en minutos, del tiempo empleado en encontrar la causa del bug en cada ticket. La media a sido alrededor de 16 minutos.}

@@

@@

@@

%\gema{Algunos de los problemas que nos hemos encontrado durante el analisis y que podrian ser resueltos de otra forma diferente a la nuestra y quizas puede que varie algo los resultados no lo se}
In studies such as Kim et al.~\cite{kim2006automatic} and Williams et al. \cite{williams2008szz} also manually analyzed samples of SZZ data. However, they report much higher percentages of correct SZZ results than in this study. The reason is that in Kim et al.~\cite{kim2006automatic} the time spends in the manual verification, in mean was 40 seconds, was lower than us, so they didn't go in depth as much as we have done. Whereas we have analyzed the whole context of a bug-fix they only focused in verify the bug-fix hunks, thus they could omit changes in the API or changes due to the evolution of the code. In the other hand, Williams et al.\~cite{williams2008szz} only took 25 random bug fix commits to manually analyze, and probably it was a small size population.
\gema{Esto es otra de las cosas que los revisores comentaron y debemos discutir: "Kim et al. [14] and Williams et al. [20] also manually analyze samples of SZZ data. However, they report much higher percentages of correct SZZ results. Potential reasons for the discrepancies should be discussed."}

In any case, our research shows evidence that assuming that the previous commit is where the cause of a bug can be found does not hold for a not insignificant percentage of bugs. Most common kind of previous commit which didn't caused the bug are:
\begin{itemize}
  \item Changes in the API, the addition of an argument in an API called.
  \item Variable renaming.
  \item Updates of SO, packages or requirements.
  \item Optimization of the code in some lines. In the context of before and after the change the code do the same, usually this kind of previous commit is in bug reports with more than one previous commit. 
  \item Gramatical bugs influenced from its previous commit. 
\end{itemize}

@@

\section{Threats to validity}
\label{sec:threats}

@@

\begin{itemize}
  \item We have not considered those tickets where the two researchers showed discordance. 
%  \begin{enumerate}
%    \item Should they discuss after their analysis to reach a better classification?, Should the tool provide this?
%    \item Does the Bug report only the same ticket classified as Bug report for all the researchers?
%  \end{enumerate}
    \item We have not taken into account errors that have been classified into \textit{Undecided}, and probably we have lost some \emph{actual} bug reports.
    \item There could be some lax criteria involving the subjective opinion of the researchers.
    \item Although the researchers are experienced programmers, they are not experts in the  OpenStack project, and their inexperience may have influenced the results of the analysis.
    \item We are only using part of the information that the tickets provide, like comments and text. There could be a recognized pattern in the data, unknown at first sight, that involves other parts of the information.
    \item We have used a random script to extract the tickets from Launchpad that have been reported during 2015. There could be unintended bias of the data, because many reasons, as for instance the phase of the project.
    \item In some cases, researchers may have classified the previous commit as the cause of the bug, even if this may not be the case (see discussion on additional conditions in if statements).
    \item Also we need add the subjectivity that could present our study.
    \gema{Debemos poner en los threats to validity la subjetividad del estudio}
\end{itemize}

@@

\section{Conclusions and Future Work}
\label{sec:conclusions}

@@

With our methodology we have identified which are real changes that introduced the bug, and this could be useful to improve the accuracy of those tools/models developed to prevent bugs. Also, the software developers stand to benefit from identifying where the bug was inserted, improving their methodology.
%How to plan to apply the knowledge in a way that can benefit software engineers.
%What are the anticipated contributions of the work?  How will you evaluate them to demonstrate usefulness?
